D3064R0: OOTA Execution is Provably Vacuous

### 2023-11-30 ootavacuous.tex
Provide prototype definition of OOTA cycle
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

>>>>

\subsection{OOTA Definition}
\label{sec:OOTA Definition}

Prior work defines ``OOTA cycle'' by example, without a precise
definition.
Sometimes ``causal cycle'' is used as if it was a definition, but
without a clear decision process for what does and does not
constitute a causal cycle..
P0442R0 defines an OOTA cycle as a fixed-point computation that is
sensitive to perturbations, which makes perfect sense to that paper's
authors, but has left others unsatisfied.

We could follow this long-established tradition of proposing
solutions to the OOTA problem without a definition of this problem.
However, we (perhaps foolishly) felt the need to provide a clear
definition.

An OOTA cycle (also known as a causal cycle) is a cycle in the
memory-model sense involving the load-buffering (LB) pattern.
Within each thread in the cycle, the value stored depends on
the value loaded.
This dependency might be a data dependency
(see Listing~\ref{lst:OOTA Cycle})
or it might be a control dependency
(see Listing~\ref{lst:OOTA Cycle Based on Conditionals}).\footnote{
	Sufficiently motivated readers should have no problem constructing
	examples involving address dependencies.}
There must be at least two distinct values such that if a given load
returns a given value, that value forces the cycle to execute so as to
cause the corresponding store's value to be equal to that given value, and
for that store to occur early enough for the load to return that value.
